Aa Language Reference Manual

### 2011-05-26 v2/Ahir-asm/devel/docs/AaLRM.tex
getting the documentation in order..  also updated release area with latest binaries and documentation.

             { sequence-of-statements}

@@

           ( expr-value  serial-statement-sequence )*
           ( default serial-statement-sequence )?

\end{verbatim}
The switch-expression is checked, and depending on its
value, one of the alternative statements is selected.
Thus, the incoming token to the switch statement is 
passed to one of the alternatives.  For example,
\begin{verbatim}
$switch a $when 0 $then a1 := (b + c)
          $when 1 $then a2 := (b - c)
          $default $null
$endswitch
\end{verbatim}
The control token is routed to the appropriate
choice sequence and if the token is not routed out 
of the block (by the {\bf place} statement 
described below), then the token passes to the
statement following the switch. 
\item If statements: An if statement has the form
\begin{verbatim}
if-statement :=
       if-spec test-expression 
           serial-statement-sequence
       (else
           serial-statement-sequence)?

>>>>

             { branch-block-statement-sequence }

@@

           ( expr-value  branch-block-statement-sequence )*
           ( default branch-block-statement-sequence )?
         end-switch-spec
The switch-expression is checked, and depending on its
value, one of the alternative statements is selected.
Thus, the incoming token to the switch statement is 
passed to one of the alternatives.  For example,
$switch a $when 0 $then a1 := (b + c)
          $when 1 $then a2 := (b - c)
          $default $null
$endswitch
The control token is routed to the appropriate
choice sequence and if the token is not routed out 
of the block (by the {\bf place} statement 
described below), then the token passes to the
statement following the switch. 
\item If statements: An if statement has the form
if-statement :=
       if-spec test-expression 
           branch-block-statement-sequence
       (else
           branch-block-statement-sequence)?
       end-if-spec
